### 2021-08-12 paper/paper.tex
fix typos

However, there are also some practical challenges associated with running MPI-based parallel
simulations with Julia. For starters, the issue of compilation times as described in the previous
section is exacerbated, as MPI runs are by default not interactive and thus compilation results cannot be cached between MPI sessions. Since this
requires to recompile everything for each subsequent execution of an MPI-parallel Julia program,
this is particularly annoying during development. Partial relief can be obtained by using
\texttt{tmpi}\footnote{\url{https://github.com/Azrael3000/tmpi}}, which allows to simultaneously
interact with multiple interactive Julia REPL sessions via the terminal multiplexer \texttt{tmux}.
However, this approach does not scale beyond a few MPI ranks and is only available on
Unix-like operating systems. The use of PackageCompiler.jl to reduce compilation times as much as
possible becomes thus mandatory. Another issue encountered when running Julia with many parallel
processes is that Julia operates with a lot of small files during startup and precompilation,
putting heavy pressure on the parallel file system. This can be partially alleviated by doing
precompilation serially, and there are tools like
\texttt{Spindle}\footnote{\url{https://github.com/hpc/Spindle}}, which help to solve similar
problems that occur when running Python programs in parallel \cite{frings2013parallelloading}.
Finally, the ease of using external libraries as desribed in Section~\ref{sec:external-libraries} is
somewhat lost when working with dependencies that themselves are parallelized with MPI. In this
case it is necessary to manually specify the paths to locally compiled libraries that have been
built against the respective system MPI installation, since there is generally no binary
compatibility between different MPI implementations. There are ongoing efforts in the Julia HPC
community to work around this limitation by using the
\texttt{WI4MPI}\footnote{\url{https://github.com/cea-hpc/wi4mpi}} wrapper package.

Even though the aforementioned difficulties do not prevent massively parallel simulations with
Julia, they raise the entry barrier for new users and developers. The overarching issue, however, is
that at the time of writing, there is little precedence in terms of openly available tutorials,
citable publications, or highly scalable example applications that can be used to learn about best
practices for MPI-based parallism in Julia. Thus, while in general it is justified to be cautiously
optimistic that most issues can be overcome, it is too early to make a final assessment on the
suitability of Julia for highly parallel simulations.

>>>>

However, there are also some practical challenges associated with running MPI-based parallel
simulations with Julia. For starters, the issue of compilation times as described in the previous
section is exacerbated, as MPI runs are by default not interactive and thus compilation results cannot be cached between MPI sessions. Since this
requires to recompile everything for each subsequent execution of an MPI-parallel Julia program,
this is particularly annoying during development. Partial relief can be obtained by using
\texttt{tmpi}\footnote{\url{https://github.com/Azrael3000/tmpi}}, which allows to simultaneously
interact with multiple interactive Julia REPL sessions via the terminal multiplexer \texttt{tmux}.
However, this approach does not scale beyond a few MPI ranks and is only available on
Unix-like operating systems. The use of PackageCompiler.jl to reduce compilation times as much as
possible becomes thus mandatory. Another issue encountered when running Julia with many parallel
processes is that Julia operates with a lot of small files during startup and precompilation,
putting heavy pressure on the parallel file system. This can be partially alleviated by doing
precompilation serially, and there are tools like
\texttt{Spindle}\footnote{\url{https://github.com/hpc/Spindle}}, which help to solve similar
problems that occur when running Python programs in parallel \cite{frings2013parallelloading}.
Finally, the ease of using external libraries as described in Section~\ref{sec:external-libraries} is
somewhat lost when working with dependencies that themselves are parallelized with MPI. In this
case it is necessary to manually specify the paths to locally compiled libraries that have been
built against the respective system MPI installation, since there is generally no binary
compatibility between different MPI implementations. There are ongoing efforts in the Julia HPC
community to work around this limitation by using the
\texttt{WI4MPI}\footnote{\url{https://github.com/cea-hpc/wi4mpi}} wrapper package.

Even though the aforementioned difficulties do not prevent massively parallel simulations with
Julia, they raise the entry barrier for new users and developers. The overarching issue, however, is
that at the time of writing, there is little precedence in terms of openly available tutorials,
citable publications, or highly scalable example applications that can be used to learn about best
practices for MPI-based parallelism in Julia. Thus, while in general it is justified to be cautiously
optimistic that most issues can be overcome, it is too early to make a final assessment of the
suitability of Julia for highly parallel simulations.
